---
title: "Evaluation of an Emprirical MP"
subtitle: "Conditioning of the Operating Model"
author: "Laurence Kell"
date: "21/03/2015"
output: html_document
---
    
# Operating Model
## Scenarios

Scenarios used for the OM were based on the 2014 stock assessment and the cross-validation (**Figure** 1). Due to the lack of convergence in the VPA and the changes catchability and relative fishing mortality-at-age in due to management in recent years the series was tuncated to end in 2008. 

A sequential t-test algorithm  (STARS;  rodionov, 2004 as modified by Szuwalski et al., 2014) was used to identify regime shifts in recruitment (**Figure** 2). The OM was conditioned so that mass, m, proportion mature and selectivity-at-age from 2009 onwards was the average from years 2006 to 2008  (**Figure** 3 shows the corresponding equilibrium curves). Recruitment in the most recent regime (1999 onwards) was given by the estimates from STARS (**Figure** 4). 

70% of FMSY is often cited as a target F. Although it will be impossible to implement in practice it does provide a basis for comparison, i.e. a counterfacual run against which simulation trials can be compared. Therefore all scenarios were projected from 2009 to 2050 for an F of 70% of FMSY (**Figure** 5). 


# Management Procedure

An empirical MP has already been run (SCRS2014-36). The issues are

* Do we also want to run a VPA MP?
* What goes in the observation error model? I was going to use the cross-validation paper to propose CPUE time series, then propose some aerial survey time series with a range of CVs due to measurement and process error.
* What about CAA? the VPA is based on age slicing which we know is biased. Do we ignore this or include ageing error in the conditioning of the OM?



# Figures

```{r, echo=FALSE}
library(knitr)

opts_chunk$set(comment   =NA, 
               fig.width =5.5, 
               fig.height=6,
               fig.path  ="../tex/",
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               cache     =TRUE)
```

```{r, echo=FALSE}
library(FLCore)
library(FLBRP)
library(plyr)
library(ggplotFL)
library(biodyn)

dirInp="/home/laurie/Desktop/Dropbox/collaboration/crossvalidation/inputs"
dirDat="/home/laurie/MEGAsync/empirical/data"

run   =c("run52013","run142013","run152013","run5JP2013",
         "run5new2013","run5westM2013","run5inflate2013")

oms=FLStocks(mlply(paste(dirInp,run,"med/bfte2014.c1",sep="/"),readVPA2Box))
oms=FLStocks(llply(oms,window,end=2008))
oms=FLStocks(llply(oms,function(x){
       stock.n(x)    =stock.n(x)/1000
       catch.n(x)    =catch.n(x)/1000
       landings.n(x) =landings.n(x)/1000
       discards.n(x) =discards.n(x)/1000

       stock.wt(x)   =stock.wt(x)/1000
       catch.wt(x)   =catch.wt(x)/1000
       landings.wt(x)=landings.wt(x)/1000
       discards.wt(x)=discards.wt(x)/1000

       catch(x)      =computeCatch(x)   
       stock(x)      =computeStock(x)  
       
       units(stock(      x))="1000 tonnes"
       units(catch(      x))="1000 tonnes"
       units(stock.wt(   x))="tonnes"
       units(catch.wt(   x))="tonnes"
       units(landings.wt(x))="tonnes"
       units(discards.wt(x))="tonnes"
       
       units(stock.n(   x))="1000s"
       units(catch.n(   x))="1000s"
       units(landings.n(x))="1000s"
       units(discards.n(x))="1000s"
       
       x}))

names(oms)=run
```

```{rom, echo=FALSE}
plot(oms)+
  kobe:::theme_ms(legend.position="bottom")+
  ylab("Year")
```

**Figure 1** Time series of recruitment, SSB, catch and fishing mortality by scenario.


```{r, echo=FALSE}
eql=FLBRPs(llply(oms,function(x){brp(FLBRP(x))}))
names(eql)=run

srs=FLSRs( llply(oms,function(x){as.FLSR(x,model="bevholt")}))
names(srs)=run
```

```{rts, echo=FALSE}
p=plot(FLQuants(llply(srs,rec)))+
  facet_wrap(~qname,ncol=2)+
  theme_bw(8)
names(p$data)[6]=".id"

stars=ldply(srs,function(x) {
              dat=as.data.frame(rec(iter(x,1)))
              biodyn:::rod(dat$data,dat$year,FALSE)})

pg=ddply(stars,.(.id,i),
         function(dat) data.frame(i=dat$i,
                                  x=with(dat,c(minyear,minyear,maxyear,maxyear)),
                                  y=with(dat,c(mn+sd,  mn-sd,  mn-sd,  mn+sd))))

# ggplot(ldply(srs, function(x) as.data.frame(rec(iter(x,1)),drop=T)))+
#   geom_path( aes(year,data))+
p+
  #  scale_x_continuous(breaks=seq(0,3000,10)) +
  #  scale_y_continuous(breaks=c(0,5,10)) +
  facet_wrap(~.id,scale="free_y",ncol=2) +
  ylab("Recruits") + xlab("Year") +
  kobe:::theme_ms(8, legend.position="none",axis.title=element_text(size=10, vjust=0.5))+
  geom_polygon(aes(x,y,group=paste(i,.id)),data=pg,alpha=.2,fill="lavender",col="blue")+
  xlab("Recruitment (1000s)")+ylab("Year")
```

**Figure 2** Time series of recruitment with regimes estimated by STARS algorithm by scenario

```{rstars, echo=FALSE}
srpar=merge(stars,ddply(stars,.(.id),with, max(as.numeric(i))))
srpar=srpar[srpar$i==srpar$V1,c(".id","mn","sd","minyear","maxyear")]
spr0=ldply(eql, function(x) as.data.frame(spr0(iter(x,1)),drop=T))
srpar=merge(srpar,spr0)
names(srpar)[6]="spr0"
srpar=transform(srpar,v=spr0*mn,s=0.9)
srpar=merge(srpar,
            ddply(srpar,.(.id), with, 
            model.frame(ab(FLPar(s=s,v=v),"bevholt",spr0)[c("a","b")]))[,-4])

## gamma, estimate rate and shape
fn1=function(mn,sd){
  rate =mn/sd^2
  shape=(sd*rate)^2
  c(rate=rate,shape=shape)}

fn2=function(shape,rate){
  mn=shape/rate
  sd=shape^0.5/rate
  c(mn=mn,sd=sd)}

srpar=merge(srpar,
            ddply(srpar,.(.id), with, 
            fn1(mn,sd)))

srDev=dlply(srpar,.(.id), with, FLQuant(rgamma(500*62,shape,rate),
                                  dimnames=list(year=1989:2050,iter=1:500))/mn)
names(srDev)=run

for(i in 1:7){
  model( eql[[i]])=bevholt()$model
  params(eql[[i]])=FLPar(unlist(srpar[i,c("a","b")]))
  eql[[i]]=brp(eql[[i]])
  }

save(eql,  file="/home/laurie/MEGAsync/empirical/data/eql.RData")
save(srpar,file="/home/laurie/MEGAsync/empirical/data/srpar.RData")
save(srDev,file="/home/laurie/MEGAsync/empirical/data/srDev.RData")

plot(FLBRPs(llply(eql,function(x) iter(x,1))),refpts=FALSE)+
  kobe:::theme_ms(legend.position="bottom")+
  xlab("")+ylab("")
```

**Figure 3** Equilibrium curves by scenario


```{rgamma,echo=FALSE}
oms=FLStocks(mlply(run,function(x)
               fwd(oms[[x]],catch=catch(oms[[x]])[,ac(1999:2008)],
                      sr   =list(model ="bevholt",
                                 params=FLPar(a=srpar[srpar[,".id"]==x,"a"],
                                              b=srpar[srpar[,".id"]==x,"b"])),
                      sr.residuals=srDev[[x]])))
names(oms)=run
plot(oms)+
  kobe:::theme_ms(legend.position="bottom")+
  ylab("Year")
```

**Figure 4** Time series of recruitment, SSB, catch and fishing mortality by scenario; values from 1999 are generated with gamma recruitment deviates sith mean and variance estimated by STARS, projected for observered catches.


```{rcounterfactual,echo=FALSE}
oms=FLStocks(mlply(run,function(x){
               om=fwdWindow(oms[[x]],end=2050,eql[[x]])
               fwd(om,
                      f    =FLQuant(0.7*c(FLBRP:::refpts(eql[[x]])["msy","harvest"]),
                                      dimnames=list(year=2009:2050)),
                      sr   =list(model ="bevholt",
                                 params=FLPar(a=srpar[srpar[,".id"]==x,"a"],
                                              b=srpar[srpar[,".id"]==x,"b"])),
                      sr.residuals=srDev[[x]])}))

names(oms)=run
save(oms,file="/home/laurie/MEGAsync/empirical/data/oms.RData")

plot(oms)+
  kobe:::theme_ms(legend.position="bottom")+
  ylab("Year")
```

**Figure 5** Counterfactual time series of recruitment, SSB, catch and fishing mortality by scenario; values from 1999 are generated with gamma recruitment deviates sith mean and variance estimated by STARS, projected for observered catches up to 2008 and for F=70% of FMSY upto 2050.
